---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include=FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# twitterbot

<!-- badges: start -->
[![R-CMD-check](https://github.com/nfrerebeau/twitterbot/workflows/R-CMD-check/badge.svg)](https://github.com/nfrerebeau/twitterbot/actions)

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- badges: end -->

This package accesses documents from the [Open Archive HAL](https://hal.archives-ouvertes.fr/) and tweets the latest scientific publications of your team (see it in action: [\@CRP2Abib](https://twitter.com/crp2abib)).
    
## Installation

You you can install the development version from [GitHub](https://github.com/) with:

```{r gh-installation, eval=FALSE}
# install.packages("remotes")
remotes::install_github("nfrerebeau/twitterbot")
```

## Usage
### Tweet your latest publications

```{r bot, eval=FALSE}
library(twitterbot)

## Set the path of the log file
## This file ensures that no document is tweeted twice
path <- file.path(Sys.getenv("HOME"), "hal.log")

## Get documents from HAL
hal <- get_hal_team(id = "399901", limit = 100)

## Post the last ten publications
msg <- post(hal, log = path, keep = 1:10)
```

You can schedule a [cron job](https://crontab.guru/) with [**cronR**](https://github.com/bnosac/cronR) or use GitHub actions to schedule tweets on a daily basis.

## Code of Conduct

Please note that the **twitterbot** project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
